\documentclass[a4paper,11pt]{article}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[english]{varioref}
\usepackage{microtype}


\DisableLigatures{encoding = *, family = * }

\pagestyle{empty}

\newcommand{\fl}[2]{(-\Delta)^{#1}#2}
\newcommand{\RR}{\mathbb{R}}

\begin{document}

\begin{flushright}
Umberto Biccari 
\\
DeustoTech, University of Deusto
\\
Avenida de las Universidades 24, 48007
\\
Bilbao, Basque Country, Spain
\\
umberto.biccari@deusto.es
\\
u.biccari@gmail.com
\end{flushright}

\begin{flushleft}
Sarah Spurgeon, Nick Karcanias and Christophe Prieur
\\
Editors in chief
\\
IMA Journal of Mathematical Control and Information
\end{flushleft}

$\newline$

\begin{flushright}
Bilbao, November 13, 2017
\end{flushright}

\noindent Dear Editors,
\\
\\
\indent Please find enclosed the manuscript of an original research work, entitled \textit{``Controllability of a one-dimensional fractional heat equation: theoretical and numerical aspects''}, which I am submitting for consideration of publication as an article in IMA Journal of Mathematical Control and Information.
\\
\indent This is a joint work with V\'ictor Hern\'andez-Santamr\'ia, from University of Deusto, Bilbao, Spain.
\\
\indent This work addresses the problem of the controllability of a one-dimensional heat equation involving the fractional Laplacian. It treats both theoretical and numerical issues. To my knowledge, the work is new, and I believe that this paper is appropriate for publication in your journal. 
\\
\indent This manuscript has not been published and is currently not submitted elsewhere.
\\
\indent Thank you for considering this work. Please, address all the correspondence concerning this manuscript to me as the corresponding author and feel free to correspond with me by email address.
\\
\\
\begin{flushright}
Sincerely yours,
\\
Umberto Biccari  
\end{flushright} 
\end{document}